---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# WEED (Wrangler for Emergency Events Database)

<!-- badges: start -->
<!-- badges: end -->

The goal of weed is to make the analysis of EM-DAT and related datasets easier, with most of the pre-processing abstracted away by functions in this package!


## Installation

You can install the released version of weed from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("weed")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rammkripa/weed")
```
# Example

This is a basic example which shows a common ``weed`` workflow:

```{r example, include=FALSE}
library(weed)
library(tidyverse)
```

# Loading the Data
```{r ex2}
em <- read_emdat("/Users/ramkripa/Desktop/Tk2.xlsx", file_data = TRUE)
```

# Locationizing the Data
```{r ex3}
locationized_data <- em$disaster_data %>%
  tail() %>%
  split_locations(column_name = "Location") %>%
  select(`Dis No`, Location,location_word, Country) %>%
  head()
locationized_data
```

# Geocoding the Locationized Data
```{r ex4}
geocoded_data <- locationized_data %>%
  geocode(geonames_username = "rammkripa")
geocoded_data
```

# How effective was our geocoding?

```{r ex5}
geocoded_data %>%
  percent_located_locations()
```
